---
title: "Index"
author: "Mario"
date: "26/01/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
```

### Number of animals Seen
```{r}
data <- read.csv("data/observations_2022.csv")
head(data)
data %>%
    group_by(RTU) %>% filter(RTU != "none") %>%
    summarise(count=n())
```
### Capture Rate
```{r}

n_total <- nrow(data)
n_hit <- data %>%
  filter(animal != 0) %>%
  nrow()

percent_capture <- (n_hit/n_total)*100

n_total ### Total Photos
n_hit   ### Total Hits
percent_capture ### Percent Capture Rate
```
# Test Wildlife Insight App Accuracy
```{r}
WI <- read.csv("images_2.csv")
WI %>%
    group_by(genus) %>% filter(genus != "NA") %>%
    summarise(count=n())
head(WI)

n_total_WI <- nrow(WI)
n_hit_WI <- WI %>%
  filter(is_blank != 0) %>%   ### The WI file give blanks 1s and hits 0s
  nrow()

percent_capture_WI <- (n_hit_WI/n_total_WI)*100

n_total_WI ### Total Photos
n_hit_WI  ### Total Hits
percent_capture_WI ### Percent Capture Rate
```
1) Capture rate by hand is 22.39% and the capture rate for WI is 22.90%

```{r}
### Step 2: Compare the 2 methods to see if they return hits and misses on the same photos.
WI_filtered <- WI %>%
  select(region, site, shrub_density, plot, cam_ID, file_name, is_blank, common_name)

combined <- left_join(data, WI_filtered, by=c("region", "site", "shrub_density", "plot", "cam_ID", "file_name"))
combined <- combined%>%
  select(-tool, -behavior, -observation, -notes)
```
### Try combining WI data to Metadata
```{r}
df <- combined%>%
  rowwise()%>%
  mutate(difference = animal-is_blank)

df <- df %>%
  filter(common_name != "Human")

n_negative <- df %>%
  filter(difference == -1) %>% 
  nrow()

n_zero <- df %>%
  filter(difference == 0) %>% 
  nrow()

n_one <- df %>%
  filter(difference == 1) %>% 
  nrow()
```


RATES:
Mario 22.2
WI 23.025

Differences Tallied"
-1 : 31   

0 : 1407

1 : 25       


```{r}
### Percent hits on cameras via human
(n_hit/n_total)*100

### Percent animals missed from WI vs visually seen
(n_one/n_hit)*100
```

```{r}
### Percent capture rate Table
Percent <- read.csv("Percent Captures.csv")
knitr::kable(Percent)
```

```{r}
### Comparison of Visual and WI processing

negative <- data.frame(n_negative)
zero <- data.frame(n_zero)
positive <- data.frame(n_one)
tally <- merge(negative, zero)
tally <- merge(tally, positive)

names(tally)[1] <- "WI Detected (-1)"
names(tally)[2] <- "Visual & WI Detected (0)"
names(tally)[3] <- "Visually Detected (1)"
knitr::kable(tally)
```



# So after cleaning everything up, and running the math, WI seems to only miss 6.8% of animal photos where compared to visually processing the photos. I think this is a good tool then